---
title: "Metaanalysis"
author: "Yelyzaveta Nemchynova"
date: "`r Sys.Date()`"
format:  
  html:
    theme: dark
    toc: true
    toc_float: true
title-block-banner: true
execute:
  echo: fenced
---

```{r}
library(readxl)
library(meta)
library(metafor)
library(dplyr)

# Import the dataset
setwd("C:/Users/lizan/OneDrive/Documents/GitHub/RRcourse2023/13. Metaanalysis")
data <- read_excel("metaanalysis_data.xlsx")

# Using metagen() function for meta-analysis using fixed effect model
fixed_model <- meta::metagen(
  TE = data$Mean_boys_play_male,
  seTE = data$SD_boys_play_male,
  studlab = data$Study,
  comb.fixed = TRUE,
  comb.random = FALSE
)

# Display the results of fixed effect model
fixed_model

```
The z-value is 7.81 and the associated p-value is less than 0.0001, indicating this result is statistically significant. This model assumes that all studies share a common effect size.

The measure I^2 is 48.7%, indicating that about 49% of the total variation across studies is due to heterogeneity rather than chance. H is 1.40, suggesting a moderate level of heterogeneity. The test of heterogeneity (Q test) has a p-value of 0.0026, indicating the presence of significant heterogeneity among the studies.

```{r}
# Using metacont() function to combine fixed and random effects
combined_model <- meta::metacont(
  n.e = data$N_boys,
  mean.e = data$Mean_boys_play_male,
  sd.e = data$SD_boys_play_male,
  n.c = data$N_girls,
  mean.c = data$Mean_girls_play_male,
  sd.c = data$SD_girls_play_male,
  studlab = data$Study,
  comb.fixed = TRUE,
  comb.random = TRUE
)

# Display the results of the combined model
combined_model
```

The heterogeneity in this model is high with I^2 at 88.0%.
**Given this result, there seems to be a significant effect of methods or quality on the results across studies.**

```{r}
# Perform random effects meta-analysis
random_model <- meta::metagen(
  TE = data$Mean_boys_play_male,
  seTE = data$SD_boys_play_male,
  studlab = data$Study,
  comb.fixed = FALSE,
  comb.random = TRUE
)

# Display the results of random effect model
random_model
```

The z-value is 6.40, and the associated p-value is less than 0.0001, indicating this result is statistically significant. This model allows for the possibility that the true effect could vary from study to study.

```{r}
# Plotting forest plot for fixed effect model, sorted by Mean_boys_play_male
forest(fixed_model, sortvar = data$Mean_boys_play_male)

# Perform meta-regression with author gender and neutral toys present as predictors
metareg_model <- metareg(random_model, ~ data$`Female authors` + data$`Neutral toys`)

# Display the results of meta-regression
metareg_model
```

The Test for Residual Heterogeneity returns a p-value of 0.5090, indicating that there is no significant residual heterogeneity. The Test of Moderators returns a p-value of < 0.0001, indicating that the moderators ("Female authors" and "Neutral toys") are significant.

This table gives the estimates of the coefficients in the model. For instance, the coefficient for "Female authors" is -76.2058 with a p-value of < 0.0001, indicating that the number of female authors is significantly associated with the effect size in the expected direction. 
**The gender of the author does have a significant effect on the results. Studies authored by females tend to show a different effect size than those authored by other gender groups.**

Similarly, the variable "Neutral toys" has a significant positive effect on the effect size.

```{r}
# Plotting funnel plot for random effect model
funnel(random_model)

# Adding contours to the funnel plot
contour_levels <- c(0.70, 0.75, 0.75)
contour_colors <- c("darkblue", "blue", "lightblue")
funnel(random_model, contour = contour_levels, col.contour = contour_colors)
legend("topright", c("p < 0.10", "p < 0.05", "p < 0.01"), bty = "n", fill = contour_colors)

```

The displayed plot reveals an asymmetrical distribution, suggesting potential publication bias or variability among the studies (heterogeneity).